No need to know: astrophysics-free gravitational-wave cosmology

### 2024-03-31 src/tex/ms.tex
[showyourwork] overleaf sync

The code used to generate all simulated data, perform the population inference, and create all figures in this paper is made publicly available at \url{https://github.com/afarah18/spectral-sirens-with-GPs}. %\GitHubURL{}, and was enabled by the \showyourwork package \citep{Luger2021}.

@@

To obtain a quantitative measure of the systematic bias introduced by mismodeling the mass distribution, we repeat the parametric analyses with 50 separate simulated catalogs of $\sim500$ events each.
We find that the broken power law model produces an overestimate of \Ho{} at greater than $1\sigma$ $\variable{output/BPL_bias_percent.txt}\%$ of the time, %whereas the \ac{GP}-based model reaches that level of bias only \result{Z}\% of the time, 
and the \plp{} model reaches the same level of bias only $\variable{output/PLP_bias_percent.txt}\%$ 
of the time.

>>>>

The code used to generate all simulated data, perform the population inference, and create all figures in this paper is made publicly available at \GitHubURL{}, and was enabled by the \showyourwork package \citep{Luger2021}.

@@

To obtain a quantitative measure of the systematic bias introduced by mismodeling the mass distribution, we repeat the parametric analyses with 50 separate simulated catalogs of $\sim1,000$ events each.
We find that the broken power law model produces an overestimate of \Ho{} at greater than $1\sigma$ $\variable{output/BPL_bias_percent.txt}\%$ of the time, %whereas the \ac{GP}-based model reaches that level of bias only \result{Z}\% of the time, 
and the \plp{} model reaches the same level of bias only $\variable{output/PLP_bias_percent.txt}\%$ 
of the time.
